\documentclass[11pt]{article}
\usepackage[a4paper,top=1in,bottom=0.53in,left=0.53in,right=0.53in]{geometry}

\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage{authblk}
\usepackage{fancyhdr}
\usepackage{hhline}
%\renewcommand{\familydefault}{\sfdefault}

\usepackage{sansmath}
\usepackage{listingsutf8}
\lstset{inputencoding=utf8x,extendedchars=\true,basicstyle=\normalfont,columns=fullflexible,breaklines=true,breakindent=0em}

\setlength\parindent{0pt}

\fancypagestyle{fancyfirst}
{
	\renewcommand{\headrulewidth}{0pt}
	\fancyhf{}
	\chead{}
	\lhead{}
	\rhead{Project ID: 124
	}
	\lfoot{}
	\rfoot{}
}

\title{\vspace{3in}adf
\\{\small Project Proposal}}
\author[]{aadsf asfd (asdf@usc.edu)}\author[]{asd fsadf (asdf@asdf.com)}
\affil[]{}
\date{}

\begin{document}
\maketitle
\thispagestyle{fancyfirst}
\pagebreak

{\bfseries What is your research question?}
\begin{lstlisting}[mathescape]
How will optimization of the automated dispensing machines (Pyxis) affect stockout percentages and dispense to refill ratios at Kaiser Permanente Baldwin Park inpatient pharmacy? 
\end{lstlisting}
\hfill

{\bfseries Please list your specific research objectives.}
\begin{lstlisting}[mathescape]
Enhance patient care and decrease costs by decreasing Pyxis stockout percentages and increasing dispense to refill ratios. 
\end{lstlisting}
\hfill

{\bfseries State the significance/background of the problem that your project addresses. Please cite a minimum of 3 references in AMA citation style used to support your background. (Approximately 300 words)}
\begin{lstlisting}[mathescape]
Pharmacy automation via automated dispensing machines (ADMs), such as Pyxis, has shown to improve pharmacy workflows by mitigating pharmacist's distributive responsibilities and efficiently expanding the distribution system in the pharmacy. However, as the use of these machines continues to evolve, there have been increasing concerns about cost, patient safety and medication access. Of particular, nursing inefficiencies in patient care have been evident with increased lines waiting for access to the Pyxis and additional phone calls following Pyxis issues, resulting in delay in care (2). Additional concerns include inefficient inventory tracking of medications in the Pyxis, resulting in Pyxis stock-outs (complete absence of medication in the Pyxis) and further delay in patient care. Through this project, we hope to improve nursing and pharmacy efficiencies at Kaiser Permanente Baldwin Park by optimizing usage of the Pyxis system, ultimately transforming to safe patient care at bedside (3). 

\end{lstlisting}
\hfill

{\bfseries Please indicate the study design that most closely describes the design of your study.}
\begin{lstlisting}[mathescape]
Regression-based observational study
\end{lstlisting}
\hfill

{\bfseries Please indicate the area of practice to which your scholarly work most closely relates.}
\begin{lstlisting}[mathescape]

\end{lstlisting}
\hfill

{\bfseries Please describe your target population and sample size for your study. Consider and respond to the following: Who are your patients? What are the inclusion/exclusion criteria? How many patients do you aim to include?}
\begin{lstlisting}[mathescape]
N/A - we will be using existing data on pyxis usage from the Pyxis Pandora System. 
\end{lstlisting}
\hfill

{\bfseries Please describe your data collection plan.}
\begin{lstlisting}[mathescape]
We will be looking at 2 key performance indicators: dispense to refill ratios \& stock-out percentages. 
\end{lstlisting}
\hfill

{\bfseries Please describe your plan for statistical analysis of your data.}
\begin{lstlisting}[mathescape]
We will be analyz
\end{lstlisting}
\hfill

{\bfseries Does your study require IRB approval? (You must discuss this with your mentor prior to submitting your proposal.)}
\begin{lstlisting}[mathescape]
No
\end{lstlisting}
\hfill

{\bfseries Please explain your rationale for why your study does or does not require IRB approval.}
\begin{lstlisting}[mathescape]
We will be analyz
\end{lstlisting}
\hfill

{\bfseries If you believe your study does require IRB approval , what category of approval will you be seeking?}
\begin{lstlisting}[mathescape]
Exempt
\end{lstlisting}
\hfill

{\bfseries Please indicate your planned date for submission to IRB}
\begin{lstlisting}[mathescape]
2018-09-14
\end{lstlisting}
\hfill

{\bfseries Please describe the specific roles and responsibilities of each student group member for this scholarly project. (It is not reasonable or acceptable to indicate that every member of your group will do every part of the project equally.)}
\begin{lstlisting}[mathescape]
Jessie Zhou: data collection, pyxis optimization and reconfiguration 

\end{lstlisting}
\hfill

{\bfseries Briefly describe the general timeline for when you will complete the following items by entering the Month and Year.}
\begin{lstlisting}[mathescape]
Prepare data collection table
06/18

Submit to IRB (if applicable)
Not applicable 

Start data collection
06/18

Finish data collection
06/18

Start data analysis
06/18

Finish data analysis
06/18

Start poster draft
06/18

Finish poster draft
06/18
\end{lstlisting}
\hfill

{\bfseries Why did you select the Project Advisor(s) for this project?}
\begin{lstlisting}[mathescape]
Dr. Chris Baek is a pharmacy supervisor at Kaiser Permanente Baldwin Park Inpatient Pharmacy and is the supervisor in charge of the pyxis optimization project. 
\end{lstlisting}
\hfill

{\bfseries Which of the following best describes how you came to work with your Project Advisor(s)?}
\begin{lstlisting}[mathescape]
Intern experience (current or past)
\end{lstlisting}
\hfill

\pagebreak
\begin{center}
	{\bfseries\large Project Advisor Section}
\end{center}

{\bfseries Thank you for agreeing to mentor one or more of our USC students on their PharmD Scholarly Project.}\\

{\bfseries Which of the following best describes your highest academic degree?}
\begin{lstlisting}[mathescape]
Bachelor's
\end{lstlisting}
\hfill

{\bfseries Which of the following describes your area of practice/work? Please check ALL that apply.}
\begin{lstlisting}[mathescape]

\end{lstlisting}
\hfill

{\bfseries Have you ever submitted research to the institutional review board (IRB)?}
\begin{lstlisting}[mathescape]
No
\end{lstlisting}
\hfill

{\bfseries What is your affiliation with the institution where the research is being conducted?}
\begin{lstlisting}[mathescape]
Emp
\end{lstlisting}
\hfill

{\bfseries Please briefly describe your previous scholarly work including research, quality improvement initiatives, publications, etc.}
\begin{lstlisting}[mathescape]
temp
\end{lstlisting}
\hfill

\end{document}